### 2013-11-08 proposal/proposal/chapter2.tex
changes

        \begin{figure}
            \begin{center}
%            \includegraphics[width=16cm]{Figures/wsarch.eps}\label{wsarch}
            \includegraphics[width=16cm]{Figures/community.eps}\label{wsarch}
            \caption{Communities of Web Services Architecture as Proposed in \cite{DBLP:journals/ijebr/MaamarSTBB09}}
            \end{center}
        \end{figure}

@@

        \subsection{Examples on Cooperative Games}\label{sec:CWSDefinition}

        An example which has closely resembles our community service model is the \emph{Single landowner and landless workers} example.
        This example was introduced in \cite{GVK369342747} and represents the \emph{landowner} entity which is providing jobs and \emph{landless workers} who cannot do anything by themselves and need to work with a landowner to gain some income.

@@

        Ketchpel introduces the Bilateral Shapley Value (BSV)\cite{conf/aaai/Ketchpel94a} for coalition games with general valaution functions.
        It reduces the combinatorial complexity of the computation of the Shapley value, breaking the community to multiple disjoint set. 
        With backtracking and dynamic programming like methods, they merge and store the marginal contribution of disjoint coalitions,
        reducing the overall complexity of the algorithm.

@@

        % THIS IS REPEATED
        In this research work, we use game theory to
        propose a cooperative game model for the aggregation of web
        services within communities. The solution concepts of our
        cooperative game seeks to find efficient ways of forming
        coalitions (teams) of web services so that they can maximize their
        gain and payoff, and distribute the gain in a fair way among all
        the web services. Achieving Fairness when the gain is distributed
        among the community members is the main factor to keep the
        coalition stable as no web service will expect to gain better by
        deviating for the community. In other words, the coalition is made
        efficient if all the members are satisfied. We first propose a
        representation function for communities of web services based on
        their QoS attributes. By using this function, we can evaluate the
        $worth$ of each community of web services. When facing new
        membership requests, a typical community master checks whether the
        new coalition having the old and new set of web services will keep
        the community stable or not. The community master will reject the
        membership requests if it finds out that the new coalition would
        be unstable, preventing $any$ subset of web services from gaining
        significantly more by deviating from the community and joining
        other communities or forming new ones. The computation of
        solutions for cooperative game theory problems is combinatorial in
        nature and proven to be NP-complete \cite{Algorithmic}, making
        this computation impractical in real world applications. However,
        using the concepts of coalition stability, we propose
        approximation algorithms running in polynomial time providing web
        services and community masters with applicable and near-optimal
        decision making mechanisms.

>>>>

        \begin{figure}
            \begin{center}
%            \includegraphics[width=16cm]{Figures/wsarch.eps}\label{wsarch}
            \includegraphics[width=16cm]{Figures/wsarch.eps}\label{wsarch}
            \caption{Communities of Web Services Architecture as Proposed in \cite{DBLP:journals/ijebr/MaamarSTBB09}}
            \end{center}
        \end{figure}

@@

        \subsection{Cooperative Game Examples}\label{sec:CWSDefinition}

        \emph {THIS EXAMPLE IT NOT COMPLETE YET}

        An example which has closely resembles our community service model is the \emph{Single landowner and landless workers} example.
        This example was introduced in \cite{GVK369342747} and represents the \emph{landowner} entity which is providing jobs and \emph{landless workers} who cannot do anything by themselves and need to work with a landowner to gain revenue (payoff).

@@

        Ketchpel introduces the Bilateral Shapley Value (BSV)\cite{conf/aaai/Ketchpel94a} for coalition games with general valaution functions.
        It reduces the combinatorial complexity of the computation of the Shapley value, breaking the community to multiple disjoint set.
        With backtracking and dynamic programming like methods, they merge and store the marginal contribution of disjoint coalitions,
        reducing the overall complexity of the algorithm. However, the solution is still NP-Complete and BSV time and space complexity grows exponentially.

@@

        % THIS IS REPEATED
        \emph {-- this is repeated --} 
        In this research work, we use game theory to
        propose a cooperative game model for the aggregation of web
        services within communities. The solution concepts of our
        cooperative game seeks to find efficient ways of forming
        coalitions (teams) of web services so that they can maximize their
        gain and payoff, and distribute the gain in a fair way among all
        the web services. Achieving Fairness when the gain is distributed
        among the community members is the main factor to keep the
        coalition stable as no web service will expect to gain better by
        deviating for the community. In other words, the coalition is made
        efficient if all the members are satisfied. We first propose a
        representation function for communities of web services based on
        their QoS attributes. By using this function, we can evaluate the
        $worth$ of each community of web services. When facing new
        membership requests, a typical community master checks whether the
        new coalition having the old and new set of web services will keep
        the community stable or not. The community master will reject the
        membership requests if it finds out that the new coalition would
        be unstable, preventing $any$ subset of web services from gaining
        significantly more by deviating from the community and joining
        other communities or forming new ones. The computation of
        solutions for cooperative game theory problems is combinatorial in
        nature and proven to be NP-complete \cite{Algorithmic}, making
        this computation impractical in real world applications. However,
        using the concepts of coalition stability, we propose
        approximation algorithms running in polynomial time providing web
        services and community masters with applicable and near-optimal
        decision making mechanisms.
